---
title: "Assignment Week 1"
output: html_document
---

### Name: Yizhen Dai

### ULCN: S2395479

```{r, echo=FALSE}
rm(list=ls(all=T)) #clears your workspace
```


# EXERCISE I. Simulating from the triangular distribution

The *triangular distribution* is the three-parameter family of distributions with probability density looking like this:

```{r, echo= FALSE} 
xa <- -1; xb <- 1; xc <- 0
plot(0, xlim = c(-2,2), ylim = c(0,1.5), type = "n", ylab = "f(x | a,b,c)" , xlab = "x",asp=1)
segments(x0 = xa, x1 = xc, y0 = 0, y1 = 1, lty = 1, lwd = 2)
segments(x0 = xb, x1 = xc, y0 = 0, y1 = 1, lty = 1, lwd = 2)

segments(x0 = xc, y0 = 0, y1 = 1, lty = 2, col = 'red')

```

The three parameters $a$, $b$ and $c$ define the $x$ values at the left, right and top position of the triangle, respectively.
In this assignment we focus on the symmetric case \(c = \frac{1}{2}(a + b)\) and even more in particular, the case \(a = -1, b = +1, c= 0\) which we will call the standard symmetrical triangular distribution.

### (a) Derivation of cdf.

Derive the cumulative distribution function \(F\) of the standard triangular distribution, and the quantile function $Q$.

Hint:

* Make life easy, calculate with \(a = -1, b = 1, c = 0\).

* Rmd allows you to type latex style text, example: \(a = \frac{1}{2}\)

* If you're not familiar with LateX, find a way to put your answer here clearly and concisely.

*Answer:*
Since it is the standard triangular distribution, \(a = -1, b = +1, c= 0\).

The cumulative distribution function \(F(x_0)\) is the area of left space surrounded by the triangle and  the vertical line \(x = x_0\). 

\[ F(x)=
    \begin{cases} 
      0 & x < -1 \\
      \frac{(x+1)^2}{2} & -1 \leq x\leq 0 \\
      1-\frac{(x-1)^2}{2} & 0 < x \leq 1 \\
      1 &  x > 1
   \end{cases}
\]

\[ Q(x)=F^{-1}(x)=
    \begin{cases} 
      \sqrt{2x} - 1 & 0 \leq x\leq 0.5 \\
      1-\sqrt{2-2x}& 0.5 < x \leq 1
   \end{cases}
\]

### (b) Draw sample.

Write R functions to generate a random sample of size \(n\) from the standard triangular distribution;

1. using the trick that the sum of the two independent uniforms has a triangular distribution,

*Answer:*
```{r}
rstdtri1 <- function(n) runif(n,-0.5,0.5)+runif(n,-0.5,0.5)

set.seed(1234)
hist(rstdtri1(40000))
```

2. using the inverse transform method,

*Answer:*
```{r}
rstdtri2 <- function(n) {
  q <- runif(n,0,1) # q
  c(sqrt(2 * q[q<=0.5]) - 1, 1 - sqrt(2 - 2 * q[q>0.5])) # <=0.5 and > 0.5
}

set.seed(1234)
hist(rstdtri2(40000))
```

3. using the acceptance-rejection method (*cf. Rizzo Example 3.7*),

*Answer:*
\(f(x) = 1 - abs(x)\)

Let \(g(x)\) be the Uniform(-1,1) density. Then \(f(x)/g(x) ≤ 2\) for all \(0 \leq x \leq 1\), so c = 2. A random \(x\) from \(g(x)\) is accepted if \(\frac{f(x)}{2g(x)}>u\), where \(u\) follows the Uniform(0,1) density.

```{r}
rstdtri3 <- function(n) {
  k <- 0 #counter for accepted 
  y <- numeric(n)
  while (k < n) {
    u <- runif(1)
    x <- runif(1,-1,1) #random variate from g 
    if ((1-abs(x)) > u) { #we accept x 
      k <- k + 1 
      y[k] <- x
    } 
  }
  y
}

set.seed(1234)
hist(rstdtri3(40000))
```


4. and last, use the functions `system.time()` and `replicate()` to compare the efficiency of these methods.

```{r}
system.time(replicate(5,rstdtri1(40000)))
system.time(replicate(5,rstdtri2(40000)))
system.time(replicate(5,rstdtri3(40000)))
```

*Answer:*
Method 1 is the most efficient one while Method 3 takes much longer time. This is not surprising since Method 3 involves much more calculation.

# EXERCISE II. Mixtures of Gaussians

$X$, $Y$ and $Z$ are independent, and normally distributed with variance 1; their means are $-1$, $1$ and $0$ respectively. Now define the following two additional random variables:

* $U = (X+Y)/2$
* $V = \begin{cases}
X&\text{if $Z<0$, and}\\
Y&\text{otherwise}.
\end{cases}$

### (a) Plot histograms
Generate a random sample from the distribution of $U$, and plot a historgram using the function `hist`. Do the same for the distribution of $V$.

*Answer:*
```{r}
n <- 400000
X <- rnorm(n,-1,1)
Y <- rnorm(n, 1,1)
Z <- rnorm(n, 0,1)
U = (X+Y)/2  #the convolution
V = c(X[Z<0],Y[Z>=0]) #the mixture

par(mfcol=c(1,2))
hist(U)
hist(V)
```

### (b) What about the distributions?
* Write down the densities of $U$ and $V$.

*Answer:*
$$
\begin{array}{l}
U:\sqrt{\frac{2}{\pi }} e^{-2x^{2}} \\
V: \frac{1}{2\sqrt{2 \pi}} (e^{-(x-1)^{2} /2}+ e^{-(x+1)^{2} /2})
\end{array}
$$

* Which of these densities is bimodal (has multiple local maxima)?

*Answer:*
V is a discrete mixture and bimodal.

* Which of these densities describes a mixture of the distributions of $X$ and $Y$?

*Answer:*
V is the mixture.

* What distribution is described by the other density?

*Answer:*
U is a 2-fold convolution.
\(U \sim N ((-1+1)/2, (1 + 1)/4)\), therefore \(U \sim N (0,0.5)\).

